\documentclass[10pt, a4paper]{article}
%\documentclass[12pt, a4paper]{article}

\usepackage{lrec2006}
\usepackage{graphicx}
%
\usepackage[utf8]{inputenc}
\usepackage{color}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{amsmath}
\usepackage{varwidth}
\usepackage{etaremune}
\usepackage{url}

\newcommand\example[1]{
    \begin{center}
        \begin{varwidth}{.9\linewidth}
            \textit{\noindent
                #1
            }
        \end{varwidth}
    \end{center}
}
\newcommand\TODO[1]{\textcolor{red}{[TODO #1]}}

\title{TermITH-Eval: a French Standard-Based Resource\\for Keyphrase Extraction Evaluation}

\name{
    Adrien Bougouin$^1$,
    Sabine Barreaux$^2$,
    Laurent Romary$^3$,
    Florian Boudin$^1$,
    Béatrice Daille$^1$
}

\address{
    $^1$~Université de Nantes, LINA, 2 rue de la Houssinière, 44322 Nantes, France\\
    $^2$~INIST-CNRS, 2, allée du parc de Brabois, 54519 Vandoeuvre-lès-Nancy, France\\
    $^3$~Humboldt-Universität zu Berlin, Dorotheenstraße 24, 10117 Berlin, Germany\\
    E-mail: adrien.bougouin@univ-nantes.fr, sabine.barreaux@inist.fr, laurent.romary@inria.fr,\\
    florian.boudin@univ-nantes.fr, beatrice.daille@univ-nantes.fr
}


\abstract{
    Keyphrase extraction is the task of finding phrases that represent the important content of a document.
    The main aim of keyphrase extraction is to propose textual units that represent the most important topics developed in a document.
    The output keyphrases of automatic keyphrase extraction methods for test documents are typically evaluated by comparing them to manually assigned reference keyphrases.
    Each output keyphrase is considered correct if it matches one of the reference keyphrases.
    However, the choice of the appropriate textual unit (keyphrase) for a topic is sometimes subjective and evaluating by exact matching underestimates the performance.
    This paper presents a dataset of evaluation scores assigned to automatically extracted keyphrases by human evaluators.
    Along with the reference keyphrases, the manual evaluations can be used to validate new evaluation measures.
    Indeed, an evaluation measure that is highly correlated to the manual evaluation is appropriate for the evaluation of automatic keyphrase extraction methods.
    ~\\~\\
    \Keywords{
        TermITH-Eval, structured resource, automatic evaluation, keyphrase extraction.
    }
}

\begin{document}
    \maketitleabstract

    \input{input/introduction.tex}
    \input{input/termith_eval_dataset.tex}
    \input{input/termith_eval_format.tex}
    \input{input/termith_eval_analysis.tex}
    \input{input/conclusion.tex}

    \section{Acknowledgments}
    This work was partially supported by the French National Research Agency (TermITH project --- ANR--12--CORD--0029) and by the French National Center for Scientific Research (GOLEM project --- grant of CNRS PEPS FaSciDo 2015, \url{http://boudinfl.github.io/GOLEM/}).

    \bibliographystyle{lrec2006}
    \bibliography{biblio}
\end{document}
